---
title: "Data Processing for Latent Variable Analysis (LVA)"
author: "Tahmeed Tureen"
date: 'League: English Premier League'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages & Source Files

Load the relevant packages and source files to perform data processing on FBref Data

Data Source: [FBref](https://fbref.com/en/) in collaboration with [StatsPerform](https://www.statsperform.com/)

Data Downloaded via [worldfootballR](https://jaseziv.github.io/worldfootballR/index.html)

```{r warning = F, message = FALSE}
library(dplyr)
library(ggplot2)
library(corrplot)
library(tidyr)
library(purrr)

source("../../1_helper_functions/fbref_helpers.R")

season <- "2022-2023"

# Read relevant data
standard_data <- readRDS(file = "../../3_data/premier_league/player_standard_stats.RDS")
poss_data <- readRDS(file = "../../3_data/premier_league/player_possession_stats.RDS")
pass_data <- readRDS(file = "../../3_data/premier_league/player_passing_stats.RDS")
pass_types_data <- readRDS(file = "../../3_data/premier_league/player_passing_types_stats.RDS")
sgca_data <- readRDS(file = "../../3_data/premier_league/player_gca_stats.RDS")
def_data <- readRDS(file = "../../3_data/premier_league/player_defense_stats.RDS")
misc_data <- readRDS(file = "../../3_data/premier_league/player_misc_stats.RDS")
shot_data <- readRDS(file = "../../3_data/premier_league/player_shooting_stats.RDS")
```

## Standard Statistics

### Process & Filter the raw data

- Create the main dataset to append additional stats onto

```{r}
# Use helper functions from 1_helper_functions/ directory
main_data <- processStandard(data_in = standard_data, season_in = season)
```

### Correlation Analysis & Distributions

```{r}
vizCorrelation(data_in = main_data)
vizContinuous(data_in = main_data)
```
\newpage

## Possession Statistics

### Correlation Analysis & Distributions

```{r}
data_in <- poss_data
season_in = season

main_data <- processPossession(main_data_in = main_data, data_in = poss_data, season_in = season)
```



## Passing Statistics

### Correlation Analysis & Distributions

```{r}
main_data <- processPass(main_data_in = main_data, 
                         data_in = pass_data, 
                         season_in = season)
```

## Pass Types

### Correlation Analysis & Distributions

```{r}
main_data <- processPassTypes(main_data_in = main_data,
                              data_in = pass_types_data,
                              season_in = season)
```
## Shooting Data

### Correlation Analysis & Distributions

```{r}
main_data <- processShots(main_data_in = main_data,
                          data_in = shot_data,
                          season_in = season)
```

## Shot & Goal Creating Actions

### Correlation Analysis & Distributions

```{r}
main_data <- processSGCA(main_data_in = main_data,
                         data_in = sgca_data,
                         season_in = season)
```

## Defending

### Correlation Analysis & Distributions

```{r}
main_data <- processDef(main_data_in = main_data, data_in = def_data, season_in = season)
``` 
## Miscellaneous

### Correlation Analysis & Distributions

```{r}
main_data <- processMisc(main_data_in = main_data,
                         data_in = misc_data,
                         season_in = season)
```

## Save Data

```{r}
saveRDS(obj = main_data, file = "../../../football_latent_variable_analysis/1_data/pl_player_stats_2223.RDS")
```


## Create a Correlation Plot

```{r}
# Drop non-numeric variables
corr_df <- main_data %>% 
    dplyr::select_if(is.numeric)

corr_df <- cor(corr_df)

write.csv(corr_df,
          file = "../../../football_latent_variable_analysis/1_data/pl_player_stats_pcorr.csv",
          row.names = TRUE)
```


