---
title: "Data Processing for Latent Variable Analysis (LVA)"
author: "Tahmeed Tureen"
date: 'League: English Premier League'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages & Source Files

Load the relevant packages and source files to perform data processing on FBref Data

Data Source: [FBref](https://fbref.com/en/) in collaboration with [StatsPerform](https://www.statsperform.com/)

Data Downloaded via [worldfootballR](https://jaseziv.github.io/worldfootballR/index.html)

```{r warning = F, message = FALSE}
library(dplyr)
library(ggplot2)
library(corrplot)
library(tidyr)
library(purrr)

source("../../1_helper_functions/fbref_helpers.R")

season <- "2022-2023"

# Read relevant data
standard_data <- readRDS(file = "../../3_data/premier_league/player_standard_stats.RDS")
poss_data <- readRDS(file = "../../3_data/premier_league/player_possession_stats.RDS")
pass_data <- readRDS(file = "../../3_data/premier_league/player_passing_stats.RDS")
pass_types_data <- readRDS(file = "../../3_data/premier_league/player_passing_types_stats.RDS")
```

## Standard Statistics

### Process & Filter the raw data

- Create the main dataset to append additional stats onto

```{r}
# Use helper functions from 1_helper_functions/ directory
main_data <- processStandard(data_in = standard_data, season_in = season)
```

### Correlation Analysis & Distributions

```{r}
vizCorrelation(data_in = main_data)
vizContinuous(data_in = main_data)
```
\newpage

## Possession Statistics

### Correlation Analysis & Distributions

```{r}
data_in <- poss_data
season_in = season

main_data <- processPossession(main_data_in = main_data, data_in = poss_data, season_in = season)
```
# Passing Statistics

```{r}


```

